Notes on the low density parameters in {\tt MAESTRO}

### 2009-06-08 docs/lo_density/lo_density.tex
updated notes

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
or equal to that particular cutoff value.  We set the coordinates at the following 
points in the code:

@@

\item In {\tt probin}, {\tt anelastic\_cutoff} and {\tt base\_cutoff\_density} are
  set to $3\times 10^6$ by default.

\item After we initialize the base state in {\tt varden}.

@@

\item After each call to {\tt correct\_base} in spherical 
  (or call to {\tt average} in plane-parallel).

@@

\item In {\tt init\_base\_state}, we abort the program if 
  {\tt anelastic\_cutoff} $<$ {\tt base\_cutoff\_density}.

\item In {\tt make\_div\_coeff}, we change how we compute {\tt div\_coeff} 
  for $r\in[{\tt anelastic\_cutoff\_coord},{\tt r\_end\_coord}]$.

\item In {\tt make\_psi} for plane-parallel, we only compute $\psi$ for 
  $r\in[{\tt r\_start\_coord},{\tt anelastic\_cutoff\_coord}-1]$.

\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt delta\_gamma1} 
  to zero for $r\in[{\tt anelastic\_cutoff\_coord},{\tt r\_end\_coord}]$.

@@

\item In {\tt init\_base\_state}, we abort the program if {\tt
  anelastic\_cutoff} $<$ {\tt base\_cutoff\_density}.

\item In {\tt base\_state}, we compute a physical cutoff location,
  {\tt base\_cutoff\_density\_loc}, which is defined as the physical
  location of the first cell-center at the coarsest level for which
  $\rho_0 <$ {\tt base\_cutoff\_density}.  This is a trick used for making
  the data consistent for multiple level problems.

\item In {\tt base\_state}, when we are generating the initial
  background/base state, if we are above {\tt base\_cutoff\_density\_loc}, 
  just use the values for $\rho,T$, and $p$ at {\tt base\_cutoff\_density\_loc}.

\item In {\tt make\_hgrhs}, {\tt make\_macrhs}, and {\tt make\_w0}, 
  we only add the volume discrepancy for
  $r\in[{\tt r\_start\_coord},{\tt base\_cutoff\_density\_coord}-1]$.

\item In {\tt mkrhohforce} for plane-parallel, for
  $r\in[{\tt base\_cutoff\_density\_coord},{\tt r\_end\_coord}]$ we
  compute $\nabla p_0$ with a difference stencil instead of simply
  setting it to $\rho_0 g$.

@@

\item In {\tt make\_grav}, if we are spherical, we do not add to the
  enclosed mass, $M(r)$ if $\rho$ is less than {\tt base\_cutoff\_density}.

\item In {\tt enforce\_HSE}, we set $p_0(r) = p_0(r-1)$ for 
  $r\in[{\tt base\_cutoff\_density\_coord}-1,{\tt r\_end\_coord}]$

>>>>

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
or equal to that particular cutoff value.  We compute the cutoff coordinate at the
coarsest level, and then set the coordinate at the next finer level to be twice that
of the coarser level.  We set the coordinates at the following points in the code:

@@

\item After we call {\tt initialize} in {\tt varden}.

@@

\item After we ``{\tt correct base}'' (by setting $\rho_0 = \overline{\rho}$ in
  plane-parallel and $\rho_0 = \rho_0 + {\bf{Avg}}(\rho - \rho_0)$).

\item At the beginning of the second-half of the algorithm (Step 6), we reset
  the coordinates using $\rho_0^n$.

@@

\item In {\tt probin}, {\tt anelastic\_cutoff} is set to $3\times 10^6$ by default.

\item In {\tt init\_base\_state}, we give a warning of {\tt anelastic\_cutoff}
  is smaller than the minimum model density.  Then, if {\tt anelastic\_cutoff} 
  $<$ {\tt base\_cutoff\_density} we abort the program.

\item In {\tt make\_div\_coeff}, for 
  $r \ge {\tt anelastic\_cutoff\_coord}$, we set
  ${\tt div\_coeff}(n,r) = {\tt div\_coeff}(n,r-1) * \rho_0(n,r)/\rho_0(n,r-1)$.

\item In {\tt make\_psi} for plane-parallel, we only compute $\psi$ for 
  $r < {\tt anelastic\_cutoff\_coord}$.
\MarginPar{I think we want to change this to include {\tt anelatic\_cutoff\_coord}.}

\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt delta\_gamma1} 
  to zero for $r \ge {\tt anelastic\_cutoff\_coord}$.

@@

\item In {\tt probin}, {\tt base\_cutoff\_density} is set to $3\times 10^6$ by default.

\item In {\tt init\_base\_state}, we give a warning of {\tt base\_cutoff\_density}
  is smaller than the minimum model density.  Then, if {\tt anelastic\_cutoff} 
  $<$ {\tt base\_cutoff\_density} we abort the program.

\item In {\tt base\_state}, we compute a physical cutoff location,
  {\tt base\_cutoff\_density\_loc}, which is defined as the physical
  location of the first cell-center at the coarsest level for which
  $\rho_0 \le {\tt base\_cutoff\_density}$.  This is a trick used for making
  the data consistent for multiple level problems.  When we are generating the 
  initial background/base state, if we are above {\tt base\_cutoff\_density\_loc}, 
  just use the values for $\rho,T$, and $p$ at {\tt base\_cutoff\_density\_loc}.
  When we check whether we are in HSE, we use {\tt base\_cutoff\_density\_loc}.

\item In {\tt make\_hgrhs}, {\tt make\_macrhs}, and {\tt make\_w0}, 
  we only add the volume discrepancy for $r < {\tt base\_cutoff\_density\_coord}$
  (in plane parallel) and if $\rho_0 > {\tt base\_cutoff\_density}$ (in spherical).
  \MarginPar{Revisit this.}

\item In {\tt mkrhohforce} for plane-parallel, for
  $r \ge {\tt base\_cutoff\_density\_coord}$, we
  compute $\nabla p_0$ with a difference stencil instead of simply
  setting it to $\rho_0 g$.

@@

\item In {\tt make\_grav} for spherical, we only add the enclosed mass if
  $\rho_0 > {\tt base\_cutoff\_density}$.

\item In {\tt enforce\_HSE}, we set $p_0(r) = p_0(r-1)$ for 
  $r \ge {\tt base\_cutoff\_density\_coord}+1$.
